Pretty darn good control: when are approximate solutions better than approximate models

### 2023-06-21 manuscript/manuscript.Rmd
created summary data for the plots, moved some of the relevant data for main text plots to manuscript_data
added main result violin plot to paper

```{r knit_global, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, echo = FALSE, message = FALSE, 
                      warning = FALSE, fig.height=5, fig.width=7.5)
library(tidyverse)
library(patchwork)
```

```{r}

```

@@

@@

We examine the trade-off between profit and sustainability faced by classical strategies in Fig. **TBD**.
Here, two quantities are plotted: the fraction of evaluation episodes of maximal length (i.e. episodes with no near-extinction events) is and the average reward obtained.
On the x-axis we have several sub-optimal constant mortality strategies that err on the conservative side: e.g. the policy labeled ‘‘80% MSY’’ has the form
\begin{align*}
  \pi: (X_t, Y_t, Z_t)\mapsto (0.8 M_X^*.\ 0.8 M_Y^*),
\end{align*}
where $(M_X^*,\ M_Y^*)$ is the optimal constat mortality strategy.
We see that sufficiently conservative policies attain high sustainability, but only at a high price in terms of profit.\footnote{
As noted before, here we equate economic profit with biomass caught.
This is done as an approximation to convey the conceptual message more clearly, and we do not expect our results to significantly change if, e.g., ‘‘effort cost’’ is included in the reward function.
When we refer to ‘‘large differences’’ in profit, or ‘‘paying dearly,’’ we mean that the ratio between average rewards is considerable---e.g. a 15\% loss in profit.
}

>>>>

```{r knit_global, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, echo = FALSE, message = FALSE, 
                      warning = FALSE, fig.height=5, fig.width=7.5)
library(tidyverse)
library(patchwork)
library(ggplot2)
```

```{r}
# read data
#frac_msy_8 <- read_csv("manuscript_data/0.8msy.csv.xz")
#frac_msy_9 <- read_csv("manuscript_data/0.9msy.csv.xz")
#frac_msy_95 <- read_csv("manuscript_data/0.95msy.csv.xz")
#frac_msy_100 <- read_csv("manuscript_data/1msy.csv.xz")
frac_msy <- read_csv("manuscript_data/frac_msy_summaries.csv.xz")

main_summaries <- read_csv("manuscript_data/comparison_3-2-var_300.csv.xz") %>%
  mutate(strategy=recode(strategy, "PPO+GP"="PPO_GP")) %>%
  arrange(strategy)

esc_ends <- read_csv("manuscript_data/esc_ends_100.csv.xz")
msy_ends <- read_csv("manuscript_data/msy_ends_100.csv.xz")
ppo_ends <- read_csv("manuscript_data/ppo300_ends.csv.xz")
gpp_ends <- read_csv("manuscript_data/gpp300_ends.csv.xz")
```

@@

```{r}
#| label: main
#| fig.cap: "Reward distributions for the four strategies considered. These are based on 100 evaluation episodes. We denote CEsc for constant escapement, CMort for constant mortality, PPO for the output policy of the PPO optimization algorithm, and PPO GP for the Gaussian process interpolation of the PPO policy."
#| out.width: "6in"
main_summaries %>% 
  ggplot() +
  geom_violin(mapping = aes(x=reward,y=strategy,fill = strategy)) +
  geom_boxplot(aes(x=reward,y=strategy, fill = strategy), width = 0.1, color = 'black', alpha=0.2)+
  theme(
    legend.position="none"
  )
```

@@

We examine the trade-off between profit and sustainability faced by classical strategies in Fig. **TBD**.
Here, two quantities are plotted: the fraction of evaluation episodes of maximal length (i.e. episodes with no near-extinction events) is and the average reward obtained.
On the x-axis we have several sub-optimal constant mortality strategies that err on the conservative side: e.g. the policy labeled ‘‘80% MSY’’ has the form
\begin{align*}
  \pi: (X_t, Y_t, Z_t)\mapsto (0.8 M_X^*,\ 0.8 M_Y^*),
\end{align*}
where $(M_X^*,\ M_Y^*)$ is the optimal constat mortality strategy.
We see that sufficiently conservative policies attain high sustainability, but only at a high price in terms of profit.\footnote{
As noted before, here we equate economic profit with biomass caught.
This is done as an approximation to convey the conceptual message more clearly, and we do not expect our results to significantly change if, e.g., ‘‘effort cost’’ is included in the reward function.
When we refer to ‘‘large differences’’ in profit, or ‘‘paying dearly,’’ we mean that the ratio between average rewards is considerable---e.g. a 15\% loss in profit.
}
